Do More Subdivisions in Wards Increase Voter Turnout? An Analysis of the 2022 Toronto Municipal Election

### 2023-06-03 outputs/paper/toronto_elections_paper.qmd
Updated script for graph to compare voter turnout and number of subdivisions

#Voter turnout by ward
#Code referenced from: https://github.com/christina-wei/INF3104-1-Covid-Clinics/blob/main/outputs/paper/covid_clinics.pdf
finalized_voter_statistics |>
  ggplot(aes(x = turnout, y = n, label = ward)) + 
  geom_point() + 
  geom_beeswarm() +
  geom_smooth(method=lm, se=FALSE) + 
  geom_text(hjust=-0.5, vjust=0.5) + 
  labs(
    title = "Number of Subdivisions vs Voter Turnout by Ward",
    x = "Turnout (%)",
    y = "Subdivisions",
    label = "Ward"
  ) 
```

>>>>

#Voter turnout by ward
#Code referenced from: https://github.com/christina-wei/INF3104-1-Covid-Clinics/blob/main/outputs/paper/covid_clinics.pdf
# & https://stackoverflow.com/questions/66652330/error-ggplot-continuous-x-aesthetic-did-you-forget-aesgroup
finalized_voter_statistics |>
  ggplot(aes(x = factor(turnout), y = n, label = ward)) +
  geom_point(aes(group = turnout)) + 
  geom_beeswarm() +
  geom_smooth(method="lm")+
  geom_text(hjust=-05, vjust=0.5) + 
labs(
    title = "Number of Subdivisions vs Voter Turnout by Ward",
    x = "Turnout (%)",
    y = "Subdivisions",
    label = "Ward"
  ) 
```
